### 2013-12-06 thesis/src/chapters/chapter-5.tex
Add additional chapter

\chapter{Architecture of Cloud-SAP}

\chapterintro{This chapter introduces architecture of Cloud-SAP, Platform-as-a-Service model that aims to satisfy requirements introduced in first chapter.}

>>>>

\chapter{Design of Cloud-SAP}

\chapterintro{This chapter introduces the high-level design of Cloud-SAP, a Platform-as-a-Service model that aims to satisfy requirements introduced in the first chapter.}
